Report for Programming Assignment 2

### 2017-11-10 Programming-Assignment-2/PA_2-report.tex
PA-2 Update 8

\section*{Instructions for the code}
\begin{itemize}
\item There are two files: \texttt{primal.py} and \texttt{dual.py}. \texttt{primal.py} concerns questions b.1, b.2 and b.4. \texttt{dual.py} concerns question b.3.
\item The programs used \texttt{CVXPY}, a convex programming module in Python.
\item To run these programs, enter \texttt{python3 <file>.py --C1 <C1-value> --C2 <C2-value>}. \texttt{<file>} can be any one of \texttt{primal} and \texttt{dual}.
\end{itemize}

@@

There is nothing specifically required to be written for the primal feasibility sub-condition, since the solution to the primal has to be naturally feasible. But using dual feasibility:
\begin{equation}
\label{dual-fease}
\alpha_{i}, \mu_{i} \geq 0 \hspace{4mm} i \in \{1, 2, \ldots, n\}
\end{equation}
\end{flushleft}

@@

Now since the primal problem \ref{primal} was a minimization problem, the dual will be a maximization problem. Using \ref{dual-objective}, \ref{dual-constraints}, we formulate the dual problem is below:
\begin{equation}
\label{dual}
\maximizewrt{\alpha \in \real^{n}} -\frac{1}{2}\alpha^{T}\xtilde\xtilde\alpha + \alpha^{T}\mathbf{1} \hspace{5mm}
\text{subject to } y^{T}\alpha = 0, \hspace{2mm} \mathbf{0} \leq \alpha_{\setS_{j}} \leq C_{j}\mathbf{1} \hspace{2mm} \forall j \in \{1, 2\}
\end{equation}

\end{flushleft}

@@

>>>>

\section*{Instructions for the code}
\begin{itemize}
\item There are two files: \texttt{primal.py} and \texttt{dual.py}. \texttt{primal.py} concerns questions b.1, b.2 and b.4. \texttt{dual.py} concerns question b.3.
\item The programs used \texttt{CVXPY}, a convex programming module in Python.
\item To run these programs, enter \texttt{python3 <file>.py --C1 <C1-value> --C2 <C2-value>}. \texttt{<file>} can be any one of \texttt{primal} and \texttt{dual}.
\item The output of \texttt{dual.py} requires the output of \texttt{primal.py} for the same parameters \texttt{C1} and \texttt{C2}. So please run \texttt{primal.py} first, and then \texttt{dual.py}. \texttt{primal.py} writes a \texttt{beta.txt} file that is used by \texttt{dual.py}, which also uses a \texttt{alpha.txt} file.
\end{itemize}

@@

Using primal feasibility:
\begin{equation}
\label{primal-fease}
\xi_{i}, y_{i}(\beta^{T}x_{i} + \beta_{0}) \geq 0 \hspace{4mm} \forall i \in \{1, 2, \ldots, n\}
\end{equation}

Using dual feasibility:
\begin{equation}
\label{dual-fease}
\alpha_{i}, \mu_{i} \geq 0 \hspace{4mm} \forall i \in \{1, 2, \ldots, n\}
\end{equation}
\end{flushleft}

@@

Now since the primal problem \ref{primal} was a minimization problem, the dual will be a maximization problem. Using \ref{dual-objective}, \ref{dual-constraints}, we formulate the dual problem is below:
\begin{equation}
\label{dual}
\maximizewrt{\alpha \in \real^{n}} -\frac{1}{2}\alpha^{T}\xtilde\xtilde\alpha + \alpha^{T}\mathbf{1} \hspace{5mm}
\text{subject to } y^{T}\alpha = 0, \hspace{2mm} \mathbf{0} \leq \alpha_{\setS_{j}} \leq C_{j}\mathbf{1} \hspace{2mm} \forall j \in \{1, 2\}
\end{equation}
\end{flushleft}

\subsection*{Question 4}
\ref{primal} is a Quadratic Programming problem and a Second Order Cone Program, whereas the dual formulation \ref{dual} is a Quadratic program.

@@

\subsection*{Question 3}
\begin{itemize}
\item If \(\alpha_{i} = 0\), then the points \(x_{i}\) don't contribute to the boundary of the margin, since we know from \ref{stationarity-beta} that \(\beta\) is dependent on \(\alpha_{i}\)s. From observation of the graph generated, this also seems to mean that these refer to the points being correctly classified.
\item if \(\alpha_{i} \in (0, C_{k}), i \in \setS_{k}\), then the \(\mu_{i} > 0 \implies \xi_{i} = 0\) from \ref{compl-slack-mu}. This means that these are \(x_{i}\)s lying on the margins of the boundaries.
\item if \(\alpha_{i} = C_{k}, i \in \setS_{k}\), then \(\mu_{i} = 0 \implies \xi_{i} \geq 0\) from \ref{compl-slack-mu}. This means that these refer to points being incorrectly classified or points on the margin of the boundary.
\end{itemize}
